---
title: "The toxAUC function"
author: "Brie Noble, Blake Langlais"
output:
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 3
vignette: |
  %\VignetteIndexEntry{The toxAUC function}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r include=FALSE}

knitr::opts_chunk$set(eval = TRUE, message = FALSE, results = 'asis', comment='')
options(width = 200)

```

# Introduction

The `toxAUC()` function gives the user a set of tools to assess incremental AUC adjusted for baseline symptoms. The accumulated area of the symptomatic AE profile above baseline can be interpreted as symptom worsening driven by treatment. Arm-level AUCs can be compared statistically using the function parameters. 


```{r}
library(ProAE)
require(knitr)
require(tidyverse)

```


In the example below, we will use the provided `ProAE::tox_acute` data
frame. This data was simulated to demonstrate a common symptomatic AE
profile where the drug group experiences acute toxicity followed by
symptom abatement over the course of treatment.

In order to use the `toxAUC()` function the data frame needs to be in
long format (multiple rows per patient). Additionally, the cycle
variable needs to be numeric. 


# Example 1 - Calculate and compare baseline adjusted incremental area under the curve by arm

```{r, results='markup'}

acute <- ProAE::tox_acute

colnames(acute)
  
```

```{r, echo=FALSE}

path = "/projects/bsi/az/proctcae/s216317.moonshot/proae/Brie_ProAE/ProAE/R/toxAUC.R"

source(path)

proctcae_vars=ProAE:::proctcae_vars

```


```{r,warnings=FALSE,results='markup'}

AUC = toxAUC(dsn = acute,
             id_var = "id",
             cycle_var = "Cycle",
             arm_var = "arm",
             baseline_val = 1,
             permute_tests = TRUE)


```

```{r}
figure_3[[3]]
```

