---
title: "The toxTables function"
author: "Brie Noble, Blake Langlais"
output:
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 3
vignette: |
  %\VignetteIndexEntry{The toxTables function}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r include=FALSE}

knitr::opts_chunk$set(eval = TRUE, message = FALSE, results = 'asis', comment='')
options(width = 200)

```

# Introduction

The `toxTables()` function produces structured statistical tables
similar to those created for CTCAE data. Tables can show arm-level
sample size and frequency distributions for PRO-CTCAE items available in
the provided data frame. P-values from chi-squared or Fisher's exact
tests can also be calculated. Additionally, risk-differences between
arms can be calculated using provided alpha-level. An R data frame is
returned in table format which can be further formatted through R
packages, spreadsheets, or directly copy and pasted into a document.

```{r}
library(ProAE)
require(knitr)
require(tidyverse)
```

In the examples below, we will use the provided `ProAE::tox_acute` data
frame. This data was simulated to demonstrate a common symptomatic AE
profile where the drug group experiences acute toxicity followed by
symptom abatement over the course of treatment.

In order to use the `toxTables()` function the data frame needs to be in
long format (multiple rows per patient). Additionally, the cycle
variable needs to be numeric. This data frame already has composite
scores calculated. If this wasn't the case then we could use the
`toxScores()` function to calculate the scores first. Alternatively, if
your data frame only included frequency/severity PRO-CTCAE items the
output would only include Frequency/Severity.

# Example 1 - Default Table

```{r, results='markup'}

acute <- ProAE::tox_acute

colnames(acute)
  
```

```{r}

path = "/projects/bsi/az/proctcae/s216317.moonshot/proae/Brie_ProAE/ProAE/R/toxTables.R"

source(path)

proctcae_vars=ProAE:::proctcae_vars

```


We can use the `toxTables()` function to create summary tables
which calculates the frequency of patients with nausea scores >= 1 and >= 3 by treatment arm.

The default summary measure used is the baseline adjusted score which is
derived by the following:

If the maximum score post-baseline is more severe than the baseline
score, then the maximum score post-baseline is used as the adjusted
score.

Otherwise, if the maximum score post-baseline is the same or less serve
than the baseline score, zero (0) is used as the adjusted score.

```{r}

table_1 <- toxTables(dsn = acute,
                    id_var="id",
                    cycle_var="Cycle",
                    baseline_val = 1,
                    arm="arm")

```

We can use the `knitr::kable()` function to see a simple RMarkdown version
of the table.

```{r}

knitr::kable(table_1$individual)

```
